Mo' Betta Gaia Distance Measurements, \\ Using Gaia + APASS photometry

### 2017-02-07 paperDistance/paperApJ.tex
added abstract

\begin{abstract}

@@

>>>>

\begin{abstract}
The Gaia TGAS Catalog contains more than 2 millions parallax measurements.
Safe conversion of a noisy parallax into a posterior belief over distances requires inference with a prior.
Usually this prior represents some kind of belief about the Milky Way.
However, there is multi-band photometry for the TGAS stars from imaging surveys.
This imaging is incredibly informative about stellar distances, as is clear from physical models of stars, and also just from looking at the data themselves.
Here we use color information on TGAS stars from [2MASS or APASS] to build a noise-deconvolved empirical prior distribution of stars in color-magnitude space.
This data-driven model contains no knowledge of the physics of stellar interiors or photospheres, nor of the Milky Way, but rather derives its precision from its generative model of noisy parallax measurements and an assumption of stationarity.
We use the Extreme Deconvolution (XD) algorithm, which is an Empirical Bayes approximation to a full hierarchical model of the true parallax and photometry of every star.
The algorithm is run not in absolute-magnitude space but in a transformed space where the measurement uncertainty is closer to Gaussian.
The XD optimized prior is used to perform parallax and distance inferences for every star, yielding a precise stellar distance estimate and uncertainty (and full posterior) for every star.
The method is capitalizing on statistical shrinkage.
Our posterior parallax estimates are more precise than the Gaia catalog outputs by a factor of [XXX] for the median TGAS star; and more precise than previous examples of Bayesian distance estimates by a factor of [YYY].
We independently validate our distances by looking at members of Milky Way star clusters; for example, M67 is not visible at all in the TGAS parallax estimates, but appears clearly in our posterior parallax estimates.
All our results, including a posterior parallax and distance sampling for [ZZZ] TGAS stars, are available in companion electronic tables.

@@

Long discussion of dust

Number of gaussians in XD, and the w parameter
